\documentclass[letterpaper]{article}

\usepackage[left=.8in,right=.8in,top=.72in,bottom=.75in]{geometry}
\usepackage[dvipsnames]{color}
\usepackage[compact]{titlesec}
\usepackage{fontspec}
\usepackage{tabularx}
\usepackage{array}

\setlength{\parindent}{0pt}

\newfontfamily\headingfont[Scale=0.9]{Oxygen}
\newfontfamily\bodyfont[Scale=0.9]{Asap}

\titleformat*{\section}{\normalfont\huge\headingfont}
\titleformat*{\subsection}{\normalfont\Large\bfseries\headingfont}
\titleformat*{\subsubsection}{\normalfont\large\bfseries\headingfont}

\titlespacing*{\section}{0pt}{.5\baselineskip}{.25\baselineskip}
\titlespacing*{\subsection}{0pt}{.5\baselineskip}{.25\baselineskip}

\newlength{\leftcol}
\newlength{\rightcol}

\setlength{\tabcolsep}{17pt}
\setlength{\leftcol}{.4\textwidth}
\setlength{\rightcol}{.6\textwidth}

\addtolength{\leftcol}{-2.0\tabcolsep}

\newcommand{\subtitle}{\normalfont\bodyfont\color{black}\large}

\renewcommand{\arraystretch}{0}

\begin{document}
\bodyfont
\large
\pagenumbering{gobble}

{\fontsize{32pt}{32pt}\bfseries\headingfont Jerome Rasky}

\vspace*{.5\baselineskip}

jyrome.112@gmail.com

(650) 394-5091

Vancouver, Canada

\begin{tabularx}{\textwidth}{@{}p{\leftcol} p{\rightcol}}
\raggedright
\vspace*{1pt}
\section*{Overview}
\subsection*{Rename}

Former NASA Software Engineer with 5 years of professional work experience. I
have experience with systems programming and administration, front-end and
back-end development, and project management.

\subsection*{Languages}

Java $\textbullet$ JavaScript $\textbullet$ Go

C++17 $\textbullet$ C11 $\textbullet$ Rust

SQL $\textbullet$ AMD64 Assembly

\subsection*{Frameworks}

React $\textbullet$ Redux $\textbullet$ Webpack

Android $\textbullet$ WordPress $\textbullet$ Django

\subsection*{Tools}

Linux $\textbullet$ Git $\textbullet$ Emacs

Bash $\textbullet$ NodeJS $\textbullet$ Mocha

\subsection*{Skills}

Systems programming

Site relability

Backend development

Frontend development

\section*{Education}

\subsection*{The University of \newline British Columbia \newline\subtitle
  Vancouver, 2014-Present}

Bachelor of Science in Computer Science, graduating 2018

\subsection*{Coursework}

Algorithms $\textbullet$ Data Structures

Operating Systems

&
\raggedright

\vspace*{2pt}

\section*{Experience}


\subsection*{New Relic \subtitle \hfill San Francisco, CA Summer 2016}

Frontend engineer working on the newly-launched Infrastructure product. Made
significant contributes, including on the backend and on other teams, which
enabled the team to meet critical milestones.

\subsection*{Arrayent \subtitle \hfill Redwood City, CA Summer 2015}

Site reliability engineer managing a large deployment of production systems.
Resolved issues in services with real-time availability requirements, and
learned to effectively monitor large-scale infrastructure.

\subsection*{NASA Ames \subtitle \hfill Mountain View, CA 2011-2014}

Full-stack developer, managing both frontend and backend codebases and
production systems. Worked closely with highly-specialized users to deliver
interfaces to meet their needs the most closely.

\subsection*{UBC CS Student Society \subtitle \hfill Vancouver, Fall 2016-Present}

Vice President External, responsible for the yearly Technical Career fair.
Practiced effective communication to coordinate a diverse team in the
organization of a complex event.

\vspace*{1pt}

\section*{Personal Projects}

\subsection*{Half2 \subtitle \hfill Algorithms $\textbullet$ Data Processing
  $\textbullet$ Filesystems }

B-tree implementation optimized nearly to match the one in the language. Started
out as a version control system, but shifted to focus more directly on data
structures.

\subsection*{Kernel \subtitle \hfill Systems $\textbullet$ Algorithms
  $\textbullet$ Memory Management}

OS kernel research project, focusing on some ideas I have about operating
systems. Prompted by a desire to learn more about operating systems and
hardware.

\subsection*{BIS2/FLX \subtitle \hfill Fuzzy Search $\textbullet$ Optimized
  $\textbullet$ Command-Line}

Highly optimized fuzzy search for terminal history. Improves over the default
search interface with better matching and a better UI. Has become something that
I use every day as an integral part of my workflow.
\end{tabularx}
\end{document}